---
title: "Introduction to the binomial R package"
author: "Levana Zhang"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```
## The Binomial Random Variable
The purpose of this package is to provide tools to help analyze statistics-related and
probability-related aspects of a binomial random variable through calculations and plots.


## bin_choose(n,k)
This function calclutates the k-combination of n elements. Inputs n and k are both numeric values


## bin_probability(success,trials,prob)
This function calculates the probability of a certain number of successes within a certain number of trials with a given probability of success.


success can be a numeric value or a numeric vector. trials and prob are numeric values.
Ex.
```{r}
bin_probability(3,5,0.5)
bin_probability(c(1:3),5,0.5)
```


## bin_distribution(trials,prob)
Determines the binomial distribution of a binomial random variable given a certain number of trials and
probability of success. trials and prob are numeric values. The function returns an object of classes 
"bindis" and "data.frame".
Ex.
```{r}
bin_distribution(5,0.5)
```


In particular, an object of class "bindis" (eg. the output of bin_distribution) can be plotted as a
bar graph.
Ex.
```{r}
a <- bin_distribution(5,0.5)
plot(a)
```


## bin_cumulative(trials,prob)
Determines the cumulative distribution of a binomial random variable given a certain number of trials 
and probability of success. trials and prob are numeric values. The function returns an object of 
classes "bincum" and "data.frame".
Ex.
```{r}
bin_distribution(5,0.5)
```


In particular, an object of class "bincum" (eg. the output of bin_cumulative) can be plotted as a
line graph with points.
Ex.
```{r}
a <- bin_cumulative(5,0.5)
plot(a)
```


## bin_variable(trials,prob)
This function, in a sense, defines a binomial random variable by storing an inputted number of trials
and an inputted probability of success. trials and prob are numeric values. trials and prob are numeric 
values. The function returns an object of class "binvar".
Ex.
```{r}
bin_variable(5,0.5)
```


In particular, an list of summary measures of an object of class "binvar" (eg. the output of
bin_variable) can be created.
Ex.
```{r}
a <- bin_variable(5,0.5)
summary.binvar(a)
```

## bin_mean, bin_variance, bin_mode, bin_skewness, bin_kurtosis
Calculates summary measures (mean, variance, mode, skewness, and kurtosis respectively) of a binomial 
random variable defined by a given number of trials and a given probability of success. Inputs are 
numeric values trial and prob (in that order). Output is a numeric value.
Ex.
```{r}
bin_mean(5,0.5)
bin_variance(5,0.5)
bin_mode(5,0.5)
bin_skewness(5,0.5)
bin_kurtosis(5,0.5)
